ICM testing

### 2023-10-24 Scripts/Paper_1.Rmd
Tuning fixes completed
Everything appears to be working A-OK now, last big fix was fixing the r value coming from the Euler-Lotka model, it needs to be exp(r) to make it = lambda, then simply used lambda in the models

# Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
#Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
# Esmarki doesn't work great as it is assessed using a quarterly model.
#Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]

years.tmp <- NULL
pnm.tmp <- NULL
waa.tmp <- NULL
ages.tmp <- NULL
rem.tmp <- NULL
mx.tmp <- NULL
NE.tmp <- NULL
vpa.tmp <- NULL
am.tmp <- NULL
mr.tmp <- NULL
all.abund.tmp <- NULL
full.abund.tmp <- NULL
for(i in Stocks)
{
  print(i)
  ASR_sub <- ASR_long %>%
    dplyr::select(Year, Stock, type, age, value) %>%
    dplyr::filter(Stock==i)

  # Drop the NA years....
  if(i == "ICES-NWWG_ICE-Summer_Clupea_harengus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1986)
  # There's some funkiness going on in the first 7 years of these data, so staring in year 8
  if( i == "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1971)
  if(i == "ICES-NWWG_FA5b_Pollachius_virens") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1982)
  if(i == "ICES-NWWG_FA5a_Pollachius_virens") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1984)
  if(i == "ICES-AFWG_NEA1-2_Pollachius_virens") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1969)
  if(i == "ICES-WGCSE_CS27.6a_Merlangius_merlangus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1980)
  if(i == "ICES-WGCSE_NS6a_Gadus_morhua") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1980)
  if(i == "ICES-AFWG_COASTNOR 1-2_Gadus_morhua") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 2006)
  if(i == "NEFSC_5Z_Pseudopleuronectes_americanus")ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1982)

@@

  nm.tmp <-  ASR_sub %>% dplyr::filter(type=="NM") %>% dplyr::rename(NM=value) %>% dplyr::select(-type)
  #minage
  minage <- min(as.numeric(nm.tmp$age[!is.na(nm.tmp$NM)]))
  if(minage == 0)  nat.mort <- nm.tmp
  # Some specials...
  if(i %in% c("ICES-WGCSE_CS7e-k_Gadus_morhua","ICES-WGCSE_ROCK6b_Melanogrammus_aeglefinus",
              "ICES-WGHANSA_SP8abd_Sardina _pilchardus","ICES-WGWIDE_NEA 1-9,12,14_Micromesistius_poutassou")) minage <- 1
  if(i == "ICES-WGWIDE_NEA 1,2,5,4a,14a_clupea_ harengus") minage <- 2
  #maxage
  maxage <- max(as.numeric(nm.tmp$age[!is.na(nm.tmp$NM)]))
  # Set up the full abundance matrix 
  full.abund <- abund
  # If we need to imput some data run this loop for natural mortality
  if(minage == 0) full.abund <- abund

  if(minage > 0)
  {
    yrs <- sort(unique((nm.tmp$Year)))
    nm.res <- NULL
    if(!i %in% c("ICES-WGCSE_CS7e-k_Gadus_morhua","ICES-WGCSE_ROCK6b_Melanogrammus_aeglefinus",
                 "ICES-WGHANSA_SP8abd_Sardina _pilchardus","ICES-WGWIDE_NEA 1,2,5,4a,14a_clupea_ harengus",
                 "ICES-WGWIDE_NEA 1-9,12,14_Micromesistius_poutassou"))
    {
      for(y in 1:(length(yrs)))
      {
        tmp <- nm.tmp %>% dplyr::filter(Year == yrs[y])
        tmp.abund <- abund %>% dplyr::filter(Year == yrs[y])
        min.nm <- tmp$NM[tmp$age == minage]
        tmp$NM[as.numeric(tmp$age) < minage] <- min.nm
        # Now save these mudders...
        nm.res[[y]] <- tmp
      } # end years loop
      nat.mort <- do.call('rbind',nm.res)
    }
  # Now do the same loopiness for abundance
    for(y in length(yrs):2)
    {
      # The minage of the natural mortality is different from minage of the abundance, annoyingly for this stock...
      if(i == "ICES-AFWG_NEA1-2_Gadus_morhua") minage <- 3
      if(i == "ICES-NWWG_ICE-Summer_Clupea_harengus") minage <- 3

      # for(a in (minage-1):0)
      # {
      #   start.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == a+1) %>% dplyr::pull(Num)
      #   nm.calc <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][a+1,]$NM) 
      #   full.abund[full.abund$Year ==yrs[y]-1,][a+1,]$Num <- start.abund/(1-nm.calc)
      # }

        #if(minage >1 & y == 1)
        #{
           # The lowest minage =4, This goes first since we go backwards, this gets us age 3 in year 3
           if(minage ==4) 
           {
               four.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == 4) %>% dplyr::pull(Num)
               nm.four <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][4,]$NM) 
               full.abund[full.abund$Year ==yrs[y]-1,][4,]$Num <- four.abund/(1-nm.four)
             #}# end my 2:0
           } # end if minage ==4

@@

  N.end <- sum(data[data$Year==max(years),]$Num)
  all.abund <- data %>% dplyr::group_by(Year) %>% dplyr::summarize(vpa=sum(Num,na.rm=T)) %>% pull(vpa)
  vpa.abund <- data %>% dplyr::group_by(Year) %>% dplyr::filter(age >= minage) %>% dplyr::summarize(vpa=sum(Num,na.rm=T)) %>% pull(vpa)
  # The real mx matrix, recruits produced per individual in each age class... Not perfect as I need to offset recruits/ssb, but close enough for the moment..

@@

  #r.p.ssb This no longer needs any offset...
  annual$r.p.ssb <- annual$recruits/annual$tot.ssb
  # recs.per.age
  data <- left_join(data, annual)
  # So I need to make an offset SSB in the 'data' object to line up with the correct r.p.ssb field.  This is probably gonna suck...
  # tmp <- NULL
  # for(j in 1:length(years))
  # {
  #   tst <- data %>% dplyr::filter(Year == years[j]) %>% dplyr::select(ssb,ssn,Year,age)
  #   tst$Year <- tst$Year + minage
  #   names(tst) <- c("ssb.offset","ssn.offset","Year","age")
  #   tmp[[j]] <- tst
  # }
  # Unpack the list
  #@ssb.off <- do.call('rbind',tmp)
  # And merge it with the data object
  #data <- left_join(data,ssb.off,by=c("Year","age"))
  data$recs.per.age <- data$ssb*data$r.p.ssb
  # mx
  # Some of the stocks are just the males and females, so these are already half the population.  Probably can just not include the male stocks in the end.
  # This works because 'males' is also in 'females'
  if(grepl("males",i)) data$mx <- data$recs.per.age/data$ssn 
  if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn/2 # Moms only! 
  data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
  # Easier to remove the years where we don't have recs.per.age...
  #data <- data %>% dplyr::filter(Year %in% years[(minage+1):length(years)])
  # Something is wrong with the decline rate method, but the exponential and logistic are working pretty... pretty... pretty good...

@@

@@

tst <- do.call('rbind',for.tune.summary)
quantile(tst$per.diff,probs=seq(0.001,1,0.001),na.rm=T)
# summary(tst$per.diff)
# summary(tst$r)
# tst <- tst[abs(tst$per.diff) > 5,]
# 
# range(tst$per.diff,na.rm=T)
# It completed 33 stocks, was on stock 34
saveRDS(back.tune.summary,"D:/Github/ICM/Results/backwards_fully_tuned_summary.Rds")
saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary.Rds")
saveRDS(back.tune.all.res,"D:/Github/ICM/Results/backwards_fully_tuned_all_res.Rds")
saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res.Rds")

@@

>>>>

# Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
#Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
# Esmarki doesn't work great as it is assessed using a quarterly model.
#Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]
#i = 'ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus'
years.tmp <- NULL
pnm.tmp <- NULL
waa.tmp <- NULL
ages.tmp <- NULL
rem.tmp <- NULL
mx.tmp <- NULL
NE.tmp <- NULL
vpa.tmp <- NULL
am.tmp <- NULL
mr.tmp <- NULL
all.abund.tmp <- NULL
full.abund.tmp <- NULL
for(i in Stocks)
{
  print(i)
  ASR_sub <- ASR_long %>%
    dplyr::select(Year, Stock, type, age, value) %>%
    dplyr::filter(Stock==i)

  # Drop the NA years....
  if(i == "ICES-NWWG_ICE-Summer_Clupea_harengus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1986)
  # There's some funkiness going on in the first 7 years of these data, so staring in year 8
  if( i == "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1971)
  if(i == "ICES-NWWG_FA5b_Pollachius_virens") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1982)
  if(i == "ICES-NWWG_FA5a_Pollachius_virens") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1984)
  if(i == "ICES-AFWG_NEA1-2_Pollachius_virens") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1969)
  if(i == "ICES-WGCSE_CS27.6a_Merlangius_merlangus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1980)
  if(i == "ICES-WGCSE_NS6a_Gadus_morhua") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1980)
  if(i == "ICES-AFWG_COASTNOR 1-2_Gadus_morhua") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 2006)
  if(i == "NEFSC_5Z_Pseudopleuronectes_americanus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1982)
  if(i == "ICES-WGNSSK_NS 4-7d_Merlangius_merlangus") ASR_sub <- ASR_sub %>% dplyr::filter(Year > 1989)

@@

  nm.tmp <-  ASR_sub %>% dplyr::filter(type=="NM") %>% dplyr::rename(NM=value) %>% dplyr::select(-type)

  #minage
  minage <- min(as.numeric(nm.tmp$age[!is.na(nm.tmp$NM)]))
  if(minage == 0)  nat.mort <- nm.tmp
  # Some specials...
  if(i %in% c("ICES-WGCSE_CS7e-k_Gadus_morhua","ICES-WGCSE_ROCK6b_Melanogrammus_aeglefinus",
              "ICES-WGHANSA_SP8abd_Sardina _pilchardus","ICES-WGWIDE_NEA 1-9,12,14_Micromesistius_poutassou")) minage <- 1
  if(i == "ICES-WGWIDE_NEA 1,2,5,4a,14a_clupea_ harengus") minage <- 2
  #maxage
  maxage <- max(as.numeric(nm.tmp$age[!is.na(nm.tmp$NM)]))

  # Now get the number of individuals in the youngest age category
  num.age.min <- ASR_sub %>% dplyr::filter(age==minage,type=="Num")
  # So any Recruitment even that is > 3 SE's away from the median I'm calling 
  # an 'extreme' recruitment event and it is going to get a lower/higher natural mortality term.
  med.mun.age.min <- mean(num.age.min$value,na.rm=T)
  sd.mun.age.min <- sd(num.age.min$value,na.rm=T)#/sqrt(length(na.omit(num.age.min$value)))
  low.rec <- med.mun.age.min - 2*sd.mun.age.min
  high.rec <- med.mun.age.min + 2*sd.mun.age.min
  high.rec.years <- as.vector(na.omit(num.age.min$Year[num.age.min$value > high.rec]))
  low.rec.years <- as.vector(na.omit(num.age.min$Year[num.age.min$value < low.rec]))
  # Set up the full abundance matrix 
  full.abund <- abund
  print(paste0("Stock ", i , ' high recruit years include ', length(c(low.rec.years,high.rec.years)), ' years'))
  # If we need to imput some data run this loop for natural mortality
  if(minage == 0) full.abund <- abund

  if(minage > 0)
  {
    yrs <- sort(unique((nm.tmp$Year)))
    nm.res <- NULL
    # These already have NM estimates at 0 so don't need to do them...
    if(!i %in% c("ICES-WGCSE_CS7e-k_Gadus_morhua","ICES-WGCSE_ROCK6b_Melanogrammus_aeglefinus",
                 "ICES-WGHANSA_SP8abd_Sardina _pilchardus","ICES-WGWIDE_NEA 1,2,5,4a,14a_clupea_ harengus",
                 "ICES-WGWIDE_NEA 1-9,12,14_Micromesistius_poutassou"))
    {
      # Just use the mean mortality of the youngest age class we have information for
      nm.use <- mean(nm.tmp$NM[nm.tmp$age==minage],na.rm=T)
      # Take the average natural mortality of the youngest age class with an m and use that
      # This avoids really blowing up the abundance in the younger age classes which can get a bit squirrly
      # nm.high.rec <- 0.5*(min(nm.tmp$NM[nm.tmp$age==minage],na.rm=T))
      # nm.low.rec <-  1.5*(max(nm.tmp$NM[nm.tmp$age==minage],na.rm=T))
      # Start by filling in everything...
      nm.tmp$NM[is.na(nm.tmp$NM)] <- nm.use
      nm.tmp <- nm.tmp[nm.tmp$age %in% 0:maxage,]
      # Now we need to fill in the 'special' cohorts that were really big (low m) or really small (high m)
      # for(y in length(yrs):1)
      # {
      #   if(yrs[y] %in% c(high.rec.years,low.rec.years))
      #   {
      #     if(yrs[y] %in% high.rec.years) nm.pick <- nm.high.rec
      #     if(yrs[y] %in% low.rec.years) nm.pick <- nm.low.rec
      #     for(a in minage:1) nm.tmp$NM[nm.tmp$Year == (yrs[y]-a) & nm.tmp$age == minage-a] <- nm.pick
      # }} #Close the if and for loops
      # Pointless rename...
    } #end the skip the stocks with nm at 0 if
      nat.mort <- nm.tmp

  # Now do the same loopiness for abundance
    for(y in length(yrs):2)
    {
      # The minage of the natural mortality is different from minage of the abundance, annoyingly for this stock...
      if(i == "ICES-AFWG_NEA1-2_Gadus_morhua") minage <- 3
      if(i == "ICES-NWWG_ICE-Summer_Clupea_harengus") minage <- 3

           # The lowest minage =4, This goes first since we go backwards, this gets us age 3 in year 3
           if(minage ==4) 
           {
               four.abund <- full.abund %>% dplyr::filter(Year == yrs[y], age == 4) %>% dplyr::pull(Num)
               nm.four <- 1-exp(-nat.mort[nat.mort$Year ==yrs[y]-1,][4,]$NM) 
               full.abund[full.abund$Year ==yrs[y]-1,][4,]$Num <- four.abund/(1-nm.four)
             #}# end my 2:0
           } # end if minage ==4

@@

  N.end <- sum(data[data$Year==max(years),]$Num)
  all.abund <- data %>% dplyr::group_by(Year) %>% dplyr::summarize(vpa=sum(Num,na.rm=T)) %>% pull(vpa)
  vpa.abund <- data %>% dplyr::group_by(Year) %>% dplyr::filter(age %in% minage:maxage) %>% dplyr::summarize(vpa=sum(Num,na.rm=T)) %>% pull(vpa)
  # The real mx matrix, recruits produced per individual in each age class... Not perfect as I need to offset recruits/ssb, but close enough for the moment..

@@

  #r.p.ssb So we are assuming the SSB in year X produces the observed recruits in year X
  annual$r.p.ssb <- annual$recruits/annual$tot.ssb
  # recs.per.age
  data <- left_join(data, annual)
  # So I need to make an offset SSB in the 'data' object to line up with the correct r.p.ssb field.  This is probably gonna suck...
  # tmp <- NULL
  # for(j in 1:length(years))
  # {
  #   tst <- data %>% dplyr::filter(Year == years[j]) %>% dplyr::select(ssb,ssn,Year,age)
  #   tst$Year <- tst$Year + minage
  #   names(tst) <- c("ssb.offset","ssn.offset","Year","age")
  #   tmp[[j]] <- tst
  # }
  # Unpack the list
  #@ssb.off <- do.call('rbind',tmp)
  # And merge it with the data object
  #data <- left_join(data,ssb.off,by=c("Year","age"))
  data$recs.per.age <- data$ssb*data$r.p.ssb
  # mx
  # Some of the stocks are just the males and females, so these are already half the population.  Probably can just not include the male stocks in the end.
  # The demographic models are 'female' only, so we'd want to divide the number of recruits by 2 and the SSN by 2, but that just cancels out
  # so there is no need to make the mom adjustment.
  data$mx <- data$recs.per.age/data$ssn # if(grepl("males",i))
  # if(!grepl("males",i))data$mx <- data$recs.per.age/data$ssn/2 # Moms only! 
  data$mx[is.nan(data$mx)] <- 0 # if we don't have any spawners in an age class in a year their fecundity is 0
  # Now for the very high recruitment years allow for a small amount of recruitment (20% of the lowest age) in the age classes after year 0....

  # if(length(high.rec.years) > 0)
  # {
  #   for(y in high.rec.years)
  #   {
  #     tmp <- data$AM[data$Year == y]
  #     am.fill <- which(tmp ==0) 
  #     if(length(am.fill) > 1) data$mx[data$Year == y-1][am.fill[-1]] <- 0.2*min(data$mx[data$Year == y & data$mx > 0],na.rm=T)
  #   }
  # }

@@

#DK PICK IT UP HERE#
# OK So the problem isn't so much "high" recruitment events, it's years in which the population abundance jumps like crash, Stock 57 (ICES Haddock NS)
# Is the best example, look at year 2005, it isn't a outlier in terms of numbers of recruits, but the population jump from 2004 to 2005 is huge and
# thus it's those years that get us the crazy fecundity numbers, which can easily be ameliorated by having a small fecundity in the age classes
# that aren't supposed to be mature yet.  Of course, is that BS, maybe!!  Ended the night running all the stocks trying to see what the changes so far brought about.

@@

#tst <- do.call('rbind',for.tune.summary)
#quantile(tst$per.diff,probs=seq(0.001,1,0.001),na.rm=T)
# summary(tst$per.diff)
# summary(tst$r)
# tst <- tst[abs(tst$per.diff) > 5,]
# 
# range(tst$per.diff,na.rm=T)
# It completed 33 stocks, was on stock 34
saveRDS(back.tune.summary,"D:/Github/ICM/Results/backwards_fully_tuned_summary.Rds")
saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary.Rds")
saveRDS(back.tune.all.res,"D:/Github/ICM/Results/backwards_fully_tuned_all_res.Rds")
saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res.Rds")

@@

```{r paper-other-metrics}

# So we agreed we wanted to look at cod, haddock, herring, and sole using the forward tuning sceanrios...

for.tune.summary <- readRDS("D:/Github/ICM/Results/forwards_fully_tuned_summary.Rds")
for.tune.all <- readRDS("D:/Github/ICM/Results/forwards_fully_tuned_all_res.Rds")

cod <- grep("morhua",names(for.tune.summary))
haddock <- grep('aeglefinus',names(for.tune.summary))
herring <- grep("harengus",names(for.tune.summary))
pollock <- grep("virens",names(for.tune.summary)) 
sole <- grep("solea",names(for.tune.summary))
euro.plaice <- grep("platessa",names(for.tune.summary))
am.plaice <- grep("platessoides",names(for.tune.summary))

p1.stocks <- sort(c(cod,haddock,herring,pollock,sole,euro.plaice,am.plaice))

Stocks <- names(for.tune.summary)
n.stocks <- length(Stocks)

for.tune.stocks <- NULL
for(i in p1.stocks) 
{
  nam <- Stocks[i]
  #  A quick way to get the other potentially interesting info for the stock...
  meta <- ASR_long[ASR_long$Stock == nam,][1,]
  tmp <- for.tune.summary[[nam]]
  tmp$Management   <- meta$Management  
  tmp$Area <- meta$Area
  tmp$Order <- meta$Order
  tmp$Family   <- meta$Family  
  tmp$Genus  <- meta$Genus 
  tmp$Species <- meta$Species
  tmp$Model <- meta$Model
  tmp$Meeting_or_reference <- meta$Meeting_or_reference
  tmp$Notes <- meta$Notes
  for.tune.stocks[[nam]] <- tmp
}

# Now unpack them...
for.tunes <- do.call("rbind",for.tune.stocks)
# Typo clean up...
for.tunes$Species[for.tunes$Species==" harengus"] <- "harengus"
# Now what does this look like...
paper.stocks <- unique(for.tunes$Stock)

# Now the doubling time simulations for each stock

dt.res <- NULL
for(i in paper.stocks)
{
  try <- for.tunes %>% dplyr::filter(Stock == i)
  double.time <- NA
  pop <- 1000

for(s in 1:100)
{
for(y in 2:100)
{
  r <- sample(na.omit(try$r),size=1)
  pop[y] <- (1+r)*pop[y-1]
} # end the years loop
tmp <- which(pop >= 2*pop[1])[1]

if(is.na(tmp)) double.time[s] <- 0
if(!is.na(tmp))double.time[s] <- tmp
} # end sim loop

dt.res[[i]] <- data.frame(dt = double.time,Stock = i,Species = try$Species[1])

} # end Stocks loop

dub.time <- do.call("rbind",dt.res)

# Now to get generation lengths + reproductive rates....
# First I need to get the fecundity and natural mortalities by cohort instead of year.

res.fin <- NULL
res.year.fin <- NULL
for(i in paper.stocks)
{
tst <- for.tune.all[[i]]
f.tmp <- tst$fecund.opt
m.tmp <- exp(-tst$nm.opt)
f.org.tmp <- tst$fecund.org
m.org.tmp <- exp(-tst$nm.org)

ages <- 0:(ncol(f.tmp)-1)
n.ages <- length(ages)
years <- tst$res$year
n.years <- length(years)
# Now I need to grab the fecundities and nat morts by cohort
if(n.years > n.ages)
{
res.cohort <- NULL
res.year <- NULL
for(y in 1:(n.years-n.ages+1))
{
  count = 0
  fs <- NA
  lx <- 1
  fs.org <- NA
  lx.org <- 1
  lx.year <- 1
  for(a in 1:n.ages)
  {
  fs[a] <- f.tmp[y+count,a]  
  fs.org[a] <- f.org.tmp[y+count,a]  
  if(a > 1) 
  {
    lx[a] <- lx[a-1] * m.tmp[y+count,a]  
    lx.org[a] <- lx.org[a-1]* m.org.tmp[y+count,a]  
    lx.year[a] <- lx.year[a-1] * m.tmp[y,a]
  }  # end the a > 1 if
  count <- count + 1
  }# end the ages loop
  res.cohort[[y]] <- data.frame(mx.opt = fs,lx.opt = lx,mx.org = fs.org,lx.org = lx.org,age = ages,
                         mx.lx.opt = fs*lx,mx.lx.org = fs.org*lx.org,
                         x.mx.lx.opt = fs*lx*ages,x.mx.lx.org = fs.org*lx.org*ages,
                         cohort=years[y],Stock = i)

  res.year[[y]] <- data.frame(mx.opt = unlist(f.tmp[y,]),lx.opt = lx.year,age = ages,
                         mx.lx.opt = unlist(f.tmp[y,])*lx.year,
                         x.mx.lx.opt = unlist(f.tmp[y,])*lx.year*ages,
                         year=years[y],Stock = i)

} # end the years loop

# unpack it...
res.fin[[i]] <- do.call('rbind',res.cohort)
res.year.fin[[i]] <- do.call('rbind',res.year)
}  # end if to make sure we have enough data to get the cohort estimates.

}# end the stock loop
res.cohort.final <- do.call('rbind',res.fin)
res.year.final <- do.call('rbind',res.year.fin)

pop.dam <- res.cohort.final %>% dplyr::group_by(cohort,Stock) %>% dplyr::summarise(gen.len.opt = sum(x.mx.lx.opt)/sum(mx.lx.opt),
                                                                gen.len.org = sum(x.mx.lx.org)/sum(mx.lx.org),
                                                                R0.opt = sum(mx.lx.opt),R0.org = sum(mx.lx.org))
pop.dam <- data.frame(pop.dam,Management=NA,Area = NA,Order=NA,
                      Family=NA,Genus=NA,Species=NA,Model=NA,Meeting_or_reference = NA,Notes = NA)

for(i in p1.stocks) 
{
  nam <- Stocks[i]
  #  A quick way to get the other potentially interesting info for the stock...
  meta <- ASR_long[ASR_long$Stock == nam,][1,]

  pop.dam$Management[pop.dam$Stock == nam]   <- meta$Management  
  pop.dam$Area[pop.dam$Stock == nam] <- meta$Area
  pop.dam$Order[pop.dam$Stock == nam] <- meta$Order
  pop.dam$Family[pop.dam$Stock == nam]   <- meta$Family  
  pop.dam$Genus[pop.dam$Stock == nam]  <- meta$Genus 
  pop.dam$Species[pop.dam$Stock == nam] <- meta$Species
  pop.dam$Model[pop.dam$Stock == nam] <- meta$Model
  pop.dam$Meeting_or_reference[pop.dam$Stock == nam] <- meta$Meeting_or_reference
  pop.dam$Notes[pop.dam$Stock == nam] <- meta$Notes

pop.dam$Species[pop.dam$Species==" harengus"] <- "harengus"

hmm <- pop.dam %>% dplyr::filter(R0.opt > 500)

hmm

hmm[hmm$Stock == "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus",]
for.tune.all$`ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus`$res

unique(hmm$Stock)
# There are 7 stocks with some bat shit happening...
# Fixed... "ICES-WGNSSK_NS4 _Solea_solea"

# These are all problems because the abundance increases like nuts in a few years....
"ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus"
"ICES-WGCSE_CS7e-k_Gadus_morhua"                  
"ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus" # Something special weird going on with this stock
"ICES-WGBFAS_WBS-25-32_Gadus_morhua"

# Figure out how to get an r of 10 and what the mx vector needs to look like for
#"ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus"

ages <- 0:12 # ages
mx <- c(0.9,500,500,rep(5000,10)) # fecundity
nat.mort <- rep(0.2,13) # natural mortality
si <- 1- nat.mort # survivial

lx <- 1
for(s in 2:(length(si))) lx[s]<-lx[s-1]*si[s-1]

eulerlotka <- function(r) (sum(lx * mx * exp(-r * ages)) - 1)^2

junk<-optimize(lower=-0.999999,upper=55,f = eulerlotka)
res <- c(junk$minimum)
res

p.start <- 10

p.end <- (1+res)*p.start
p.end

R0 <- sum(lx*mx)
R0

tmp <- for.tune.all[["ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus"]]
tmp$nm.org
tmp$fecund.opt
t1 <- vpa.tmp$`ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus`
range(t1[2:length(t1)]/t1[1:(length(t1)-1)])
# So using all the age classes actually reduces the ratios from year to year requiring less insanity...
t2 <- all.abund.tmp$`ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus`
range(t2[2:length(t2)]/t2[1:(length(t2)-1)])

data.frame(tmp$res$year,tmp$res$vpa.abund,t1,t2)

mx <- c(0,0,0,rep(30,11))
nm <- rep(0.2,14)

```{r simp-figs}

ggplot(for.tunes) + geom_jitter(aes(y=r,x=Species)) + scale_y_continuous(name = 'rate of growth (r)',breaks = c(-1,-0.5,0,0.5,1:10),limits = c(-1,3))

ggplot(for.tunes) + geom_jitter(aes(y=r.vpa.init,x=Species)) + scale_y_continuous(name = 'rate of growth (r)',breaks = c(-1,-0.5,0,0.5,1:10),limits = c(-1,3))

unique(for.tunes$Species)
windows(11,11)
ggplot(dub.time) + geom_jitter(aes(y=dt,x=Species),alpha=0.05,fill="black",color="black",shape=22) + 
                   scale_y_continuous(name = 'Doubling time (years)',breaks = seq(0,100,by=5))

ggplot(for.tunes) + geom_density(aes(r,group=Species,color=Species,fill=Species),alpha = 0.2)

windows(11,11)
ggplot(pop.dam) + geom_boxplot(aes(y=gen.len.opt,x=Species)) + ylab("Generation Length (years)")

options(scipen=999)
ggplot(pop.dam) + geom_boxplot(aes(y=R0.opt,x=Species))  + scale_y_log10(name = "Lifetime Reproductive Output",
                                                                         breaks = c(0.001,0.01,0.1,1,5,10,50,100,500,1000,5000,1e4,1e5,1e6),
                                                                         minor_breaks = NULL)
